### 2019-08-14 README.Rmd

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mcguinlu/robvis?branch=master&svg=true)](https://ci.appveyor.com/project/mcguinlu/robvis)
[![metaverse Identifier](https://img.shields.io/static/v1.svg?label=Part%20of%20the&message=metaverse&color=informational)](https://www.github.com/rmetaverse/metaverse)

>>>>

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mcguinlu/robvis?branch=master&svg=true)](https://ci.appveyor.com/project/mcguinlu/robvis)
[![Codecov test coverage](https://codecov.io/gh/mcguinlu/robvis/branch/master/graph/badge.svg)](https://codecov.io/gh/mcguinlu/robvis?branch=master)
[![metaverse Identifier](https://img.shields.io/static/v1.svg?label=Part%20of%20the&message=metaverse&color=informational)](https://www.github.com/rmetaverse/metaverse)
